---
title: "simpleRegress"
author: "Sasha Sanchez"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


We are going to find the model length of the BEARS based on chest. 


```{r}
mychest<- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(mychest)
summary.lm(mychest)
```

This MYCHEST model is using chest compared to the first model using neck in the this model the adjusted r squared is 0.786 and the residual standard error is 4.939. In the SIMP model the adjusted r squared was 0.747 and the following residual standard error was 5.376. Which is more better becuase it explains for of the error. In this case the error is smaller.    


```{r}
myheadw<- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(myheadw)
summary.lm(myheadw)
```


In the model myheadw the adjusted r squared has gone down and the residual standard error has gone up.



```{r}
myheadlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(myheadlen)
summary.lm(myheadlen)
```


In this model myheadlen the adjusted r squared is 0.843 and the residual standard error is 4.235. Comparing all the models so far this one shows a much better prediction. 





